|

### 2025-01-31 doc/paper.qmd
pap

**Step 2: Data Preparation**  
The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021. To ensure consistency with @EC_Report_2024, the abbreviation 'GR' for Greece was replaced with 'EL' in the trans_report_auditor_state field, affecting 188 rows.

The `number_of_disclosed_pies` variable provides the clearest indication of statutory audits conducted by each auditor for PIEs. The definition of PIEs varies across EU and EEA countries [@AccountancyEurope_PIE_2017], but if Transparency Reports consistently follow country-specific definitions, using the provided variable is reasonable. An important verification step involved comparing the reported `number_of_disclosed_pies` with the count of unique `entity_map_fkey` entries for each `transparency_report_fkey`. This analysis revealed that 5,696 transparency reports included fewer entities in the dataset than the disclosed PIEs, suggesting that some PIE entities might be missing from the dataset. This discrepancy reflects missing PIE data rather than the inclusion of non-PIE entities, hence it is assumed that all entities in the dataset are PIEs, maintaining consistency in the framework for analysis.

Additionally, missing values in key fields, including `transparency_report_fkey`, `entity_map_fkey`, `auditor_fkey`, and `trans_report_auditor_state`, were checked, and it was confirmed that no rows needed to be removed due to missing data, ensuring the completeness of the dataset. To focus on relevant data, rows with `number_of_disclosed_pies` equal to or less than zero were filtered, but no such rows were identified, and all observations were retained.

Duplicate entries in the `entity_map_fkey` column were then analyzed, revealing 1,011 duplicate entities. I assume that duplicate entries in the dataset do not introduce significant issues for the replication of Figure 3. Duplicate entries for the same entity are expected in cases where an entity is audited by multiple audit firms or networks, potentially as part of a joint audit. Since these duplicates retain consistent information on `trans_report_auditor_state`, they do not distort country-level distributions. Additionally, while duplicates might expand representation across different auditor networks or groups, the essence of Figure 3 — focusing on aggregate distributions — remains unaffected. Therefore, these duplicates were not removed.

Auditor network names were standardized to ensure consistency, with names like `|Mazars Worldwide|Praxity Global Alliance|` simplified to `|Mazars Worldwide|`, for example. This standardization helped avoid double-counting and unify same entries under consistent naming conventions.

Audit firms were then categorized into groups, including the Big 4 (Deloitte, EY, KPMG, and PwC), the 10KAP (which includes the Big 4 along with other major networks listed in @sec-research_design_assumptions), 'Unaffiliated' firms (those outside the Big 4 and 10KAP). The `auditor_network` field contained 636 observations with missing values, which were grouped under the “Other (Blank)” category. I assume that these blank entries do not belong to the Big Four or 10KAP networks but may still contribute to the CR4 category in some countries. So, these entries were retained in the dataset and reviewed during the aggregation stage to validate their relevance.

These preparation steps ensured alignment with the methodology of @EC_Report_2024 and the dataset’s readiness for subsequent analysis.

>>>>

**Step 2: Data Preparation**  
The merged dataset would integrate stock return data from CRSP (`crsp_daily_stock_returns`), firm fundamentals from Compustat (`compustat_fundq_1972_2023`), and the CRSP-Compustat linking table (`linkdata_compustat_crsp.parquet`). The `PERMNO` identifier from CRSP and `GVKEY` from Compustat are connected via `LPERMNO` in the linking table, ensuring correct firm-year alignment. Unnecessary variables from linked table, such as `linkprim`, `liid`, `linktype`, and `usedflag`, are dropped. The resulting dataset would retain only daily stock returns (`ret`), earnings announcement dates (`rdq`), fiscal year-end indicators (`fyr`), and firm identifiers (`permno, gvkey`), used further for BHR calculation and regression analysis.

After defining the event windows for each earnings announcement day in Q1-Q4, retain only the firms that have four earnings announcements per year, such that each of them falls within the same calendar year. Additionally, for the subgroup replication of Table 2 Panels C-D classify the firms based on their fiscal year-end (`fyr`) to define whether firms have December fiscal year-end firm or in any another month.
